A Review of the Movie \textit{Apocalypse Now}

### 2015-11-16 paper.tex
References in Alphabetical order
Udated Abstract

\abstract{This paper will explore the applications of Abnormal Psychology in the film \textit{Apocalypse Now}, including correct and incorrect aspects of symptoms, diagnosis, and other disorders that are depicted in the movie. Using the DSM-V as the source for determining the accuracy of disorders, the characters in the film, primarily Captain Benjamin L. Willard and Colonel Walter E. Kurtz, will be thoroughly examined to outline which disorder, or disorders, they exhibit and which the film may inaccurately depict. Because the film is based in the Vietnam War, the perspective when analyzing the characters will be shifted to fit the setting, thus potentially causing a diagnosis to be different than the diagnosis of a “normal” life experience.}

@@

\raggedbottom
\pagebreak
\subsection{References}

>>>>

\abstract{\textit{Apocalypse Now} is a film directed by Francis Frank Coppola. It follows the main character, Captain Benjamin L. Willard, through his last mission in Vietnam. Assigned with assassinating the rogue Captain Walter E. Kurtz, he accompanies 4 other crew members, Chief, Chef, Clean, and Lance, through the chaos of the Vietnam War. The film dives into the dark progression of these characters, and how the mission Willard is assigned and so desperate to finish affects them and those they encounter, friend or foe. This paper will explore the applications of Abnormal Psychology in the film , including correct and incorrect aspects of symptoms, diagnosis, and other disorders that are depicted in the movie. Using the DSM-V as the source for determining the accuracy of disorders, Willard, Chef, and Lance will be examined to outline which disorder, or disorders, they exhibit and which the film may inaccurately depict. Because the film is based in the Vietnam War, the perspective when analyzing the characters will be shifted to fit the setting, thus potentially causing a diagnosis to be different than the diagnosis of a “normal” life experience.}

@@

\raggedbottom
\pagebreak
\section{References}
